---
title: "Reproducible Research: Peer Assessment 1"
output: 
  html_document:
    keep_md: true
---

## Loading and preprocessing the data

Unzip and load current data
```{r}
unzip("activity.zip")
activity <- read.csv("activity.csv")
```


## What is mean total number of steps taken per day?

Calculate total steps per day and look at distribution.
```{r}
totalSteps<-aggregate(steps~date,data=activity, FUN = sum,na.rm=TRUE)
hist(totalSteps$steps, xlab = "Total Steps per day")

```

Calculate mean and median of total steps
```{r}
mean(totalSteps$steps)
median(totalSteps$steps)

```


## What is the average daily activity pattern?

Calculate mean steps per 5 min interval and plot time series.

```{r}
stepsInterval <- aggregate(steps ~ interval, data = activity, FUN = mean, na.rm = TRUE)
plot(steps ~ interval, data = stepsInterval, type = "l")

```

Which 5-minute interval, on average across all the days in the dataset, contains the maximum number of steps? (Starting at min #:)
```{r}
maxInterval <- stepsInterval[which.max(stepsInterval$steps),"interval"]
maxInterval

```


## Imputing missing values



## Are there differences in activity patterns between weekdays and weekends?
